\documentclass[10pt,a4paper]{article}

\setlength{\oddsidemargin}{-0.2in}
\setlength{\evensidemargin}{-0.2in}
\setlength{\topmargin}{-0.8in}
\setlength{\textheight}{9.9in}
\setlength{\textwidth}{7.2in}
\setlength{\parskip}{1.5ex plus 0.5ex minus 0.5ex}


\begin{document}

\pagestyle{empty}

\flushleft{\huge{John Doe -Theoretical Makanga}}
\vspace{0.1cm}
\begin{tabular}{p{12.6cm}p{4.5cm}}
\hline \\
{\em Address:} 24021 Koinange & {\em Email:}
\small{samplemail@sample.com} \\ 
\hspace{1.3cm} Nairobi, Kenya & {\em Phone:}
\small{+254-712345678} \\
%\vspace{0.1cm}
\hline
\end{tabular}

\vspace{-0.3cm}
\section*{Summary}
\vspace{-0.21cm}
Brief summary about yourself in the depart of wherever you are. Just explain yourself well in a way that the reader we'll want to read more about your and get interest in asking you for an Interview.
I wrote this C.V sample as a way to understand the formaating and usage of LaTex. Have a fab day.
\vspace{-0.2cm}
\section*{Education}
\vspace{-0.22cm}
\begin{itemize}

\item {\bf Doctor of Philosophy(PHD) i Human Anatomy}  (\emph {Jan 2019 --
  February 2030}) \\
{\sc {\bf Makerere University, Mogadishu}} \\
\emph{Grade Point Average:} 4.5 out of 5.0

\item {\bf Master of Science in Mechatronic Engeneering}  (\emph{September 2018 --
    May 2019}) \\
{\sc {\bf Computer Engeneering, University of
    California, USA}} \\
%\emph{Grade Point Average:} list here

\item {\bf Bachelor of Technology}  (\emph{June 2001 -- June 2005}) \\
{\sc {\bf Lord of Rings Uiversity,
    Zanzibar}} \\
\emph{Honors:} $1^{st}$ rank in 2012-Feb and $2^{nd}$ rank in 2015-Aug
in the university 
\end{itemize}


\vspace{-0.6cm}
\section*{Personal Project}
\vspace{-0.18cm}

{\sc {\bf ROBOTICS Movements at MIT} \emph{(January 2016 - February 2018)}}\\
\begin {itemize}
\setlength{\itemsep}{-1pt}

\item {\bf {Project topic:} Creating a robot automator Ipsum ipsum} \\
\emph {Languages:} JAVA, Python, C \\
\emph {Frameworks:} Bootstrap, Ipsum, Lorem \\

\item {\bf {Project details}} 

\begin {itemize}
 \vspace{-0.1cm}
\setlength{\itemsep}{-1pt}
\item This is where the projects details will listed.

\item More about the project.

\item The robotic more info. 



\end {itemize}

\item {\bf {Article Publications}}
\begin {itemize}
 \vspace{-0.1cm}
\setlength{\itemsep}{-1pt}

\item A changed world, looking into robotics \emph {Accepted at HackerNews, March 2018} \\

\item This is another publication \emph {Accepted at this blog or somewhere else, September 2018} \\ 

\end {itemize}





\item {\bf {Internship:} This Indeustry, Country} \emph {(Jun 2018 - Aug 2019, Jun 2019 - Jul 2020)} \\


\begin {itemize}
 \vspace{-0.1cm}
\setlength{\itemsep}{-1pt}

\item About what you were doing or specializing in.

\item More Info about the duties or course.

\end {itemize}



\end {itemize}

\vspace{-0.6cm}
\section*{Professional Experience}
\vspace{-0.12cm}

{\sc {\bf Safaricom Co. Limited Company} \emph{(July 1913 -- April 2018)}}\\ 
\emph{Supervisor:} Samahani Mteja wa nambari \\
\vspace{0.12cm}

\begin{itemize}
\setlength{\itemsep}{-2pt}
\item {\bf Network Engineer} \emph{(February 1913 -- April 2000)} \\

% \begin{itemize}

%\setlength{\itemsep}{8pt}

 {\bf  {Roles and Responsibilities:}}
 \vspace{-0.2cm}
\begin {itemize}
\setlength{\itemsep}{-1pt}
\item Role one in the company. 
\item About the role.
\item More about the role as as you'd like.
\end{itemize} 
%\emph{Supervisor:} Prof. Eduardo Tovar \\
\vspace{-0.1cm}

 {\bf Selected Projects:}
\vspace{-0.2cm}
\begin{itemize}

\item {\bf Currency Converter}
  \emph{(February 2005 -- May 2007)} \\ 
\vspace{-0.08cm}
\begin{itemize}
\setlength{\itemsep}{-1.0pt}
\setlength{\itemindent}{-10pt}
\setlength{\parindent}{-10pt}
\item Created the converter to deal with euro-bond
\item more about the project. 
\item A little more about the project.  
\end{itemize}
\setlength{\parindent}{0pt}



%\This is a comment

\pagebreak [4]


\setlength{\parindent}{0pt}


\end{itemize}

\item {\bf Google Intern} \emph{(Jan 2017 -June 2018)} \\
{\sc {\bf Google, Inc.}} \\  
\emph{Supervisor:} Dr. Jack Ma \\
\vspace{-0.1cm}
\begin{itemize}
\setlength{\itemsep}{-2pt}
\setlength{\itemindent}{-10pt}
\setlength{\parindent}{-10pt}
\item Worked on AI project ipsum ipsum \\ \indent and Plant automator.  
%\item 1 end
%  item 2
\item One-on-one experience working with Elon Mask Karanja and jack on Neurons.
\end{itemize}
\setlength{\parindent}{0pt}

\item {\bf Computer Engineering Intern} \emph{(May 2018 -July 2019)} \\
{\sc {\bf Airtel Company, Nairobi}} \\  

\vspace{-0.1cm}
\begin{itemize}
\setlength{\itemsep}{-2pt}
\setlength{\itemindent}{-10pt}
\setlength{\parindent}{-10pt}
\item Studied unit processes, control systems, scale-up
  methods, risk analysis methods and Unit testing.
%\item Performed 
\item Worked with cross-functional teams to gain hands-on experience
  in security measurements, control and \\ \indent regulations.
\end{itemize}

\setlength{\parindent}{0pt}

\end{itemize}

%\setlength{\topmargin}{0in}

\markright{\hspace{14.2cm} Abhiruchi Gadgil, Page}
\pagestyle{myheadings}

\vspace{-0.65cm}
\section*{Professional Courses}

\begin{itemize}
\item {\bf Web Developement} \\
\vspace{-0.1cm}
\begin{itemize}

\item {\bf Frontend Development:} Course designed by github Academy
  more about the course.

\item {\bf backend development (ISACA, ZA):}
  Detailed coverage abut the project.  

%\item skill 2
\end{itemize}

\item {\bf Modelling} \\
\vspace{-0.1cm}
\begin{itemize}

\item {\bf Computer Modelling:} More information about the course. 


\item {\bf Game Modelling:} More info about the course unit.
 


\end{itemize}

\end{itemize}
\vspace{-0.65cm}

%\section* {Other Relevant Projects to be listed}



\section*{Affiliations}

\begin{itemize}
\item {\bf Affiliations} \\
\vspace{-0.08cm}
\begin{itemize}

\item {\bf Volunteer and USAID:} Imagin8ors - EdTech start-up (2017-2018), Courage Center, Minneapolis (2011 - 2012), Greater Philadelphia Cares, an NGO
  in Philadelphia, USA (2006-2007).  
 
\item {\bf Technical Officer @ UN:} More information .e.g. place and year (2008-2012).  

\item {\bf Computer Analyst:} More info about it (2018).  

\end{itemize}

\item {\bf Activities} \\
\vspace{-0.08cm}
\begin{itemize}

\item Prize for best ``Course developer'' for a working model in the contest
  Contraption at Hackerfest 2005, Lean, Germany.   

\item Second activity details goes here in the same method as one. 

\item Third activity details goes here in the same manner as one.  

% Any additional activity should be  added as above

\item Fourth activity details goes here as above.

\end{itemize}

\end{itemize}

\vspace{-0.08cm}
\section*{Additional Information}

\vspace{-0.1cm}
\begin{itemize}

\item {\bf Key Skills:} Pen testing, Web programming. %add more skills here

\item {\bf Nationality:} Japanase. %add nationality here

\item {\bf Relevant language skills:} English (Fluent), Japanase
  (Beginner), Kikuyu and Frech (Native).
  
\item {\bf Interests:} Programming related initiatives, blogging, classical music.

\item {\bf Hobbies:} Mountain Climbing, article Writing, Swimming. %add more hobbies

\end{itemize}


\section*{References}

\vspace{-0.08cm}
\begin{itemize}

\item Jack Ma - Alibaba, Kenya 
\item May Atieno- CEO, sample company, location.

\end{itemize}

\end{document}
